Designing an Agent for an Active Guidance System for Object Search

### 2018-11-13 paper.tex
Refined text and plots after edit suggestions

\title{Designing an Active Vision Indoor Object Search Guidance System}

@@

\abstract{In this work, we propose an active vision system that uses a Markov Decision Process and mobile phone to enable a user to find an object in an unknown environment. An initial implementation of this system was implemented and tested with a set of experiments were carried out with sighted participants to determine the effectiveness of the system. We found that the system works reasonably well and compares well to similar systems. }

@@

\begin{equation}
  a = \langle{}s\rangle, a\in{}\mathbf{A},
\end{equation}
\uline{and the possible actions are}

@@

\uline{We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}). A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function. The MDP therefore has a total of 144 reachable states ($8\times9\times2$).}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{figures/system_screenshot.png}
  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
  \caption{A picture of the environment used for the experiments. Each QR code represents an object. OVERLAY GRID AND PRESENT EXAMPLE SEARCH}\label{fig:env-picture}
\end{figure}

>>>>

\title{Designing an Agent for an Active Guidance System for Object Search}

@@

\abstract{In this work, we propose a Markov Decision Process-based system that generates guidance instructions for a user to find a target object in an unknown environment and forms part of an active vision indoor guidance system for the visually impaired. An initial implementation of this system was implemented in an Android app and a set of experiments were carried out with sighted participants to determine its effectiveness. We found that the system works reasonably well and compares well to similar systems. }

@@

\begin{equation}
  a = \langle{}s\rangle, a\in{}\mathbf{A},
\end{equation}
and the possible actions are

@@

We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}). A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function. The MDP therefore has a total of 144 reachable states ($8\times9\times2$).

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/system_screenshot2.png}
  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
  \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
\end{figure}
